### 2015-12-11 paper/abstract.tex
Review
Proofread abstract

With the ever increasing complexity of simulation models, parallel simulation
becomes necessary to perform the simulation within reasonable time bounds.
The built-in parallelism of Parallel DEVS is often insufficient to tackle this
problem on its own. Several synchronization algorithms have been proposed,
each with a specific kind of simulation model in mind. Due to the significant
differences between these algorithms, current Parallel DEVS simulation tools
restrict themself to only one such algorithm. In this paper, we present a
Parallel DEVS simulator, grafted on C++11, which offers both conservative and
optimistic simulation. We evaluate the performance gain that can be obtained
by choosing the most appropriate synchronization protocol. Our implementation
is compared to ADEVS using hardware-level profiling on a spectrum of benchmarks.

>>>>

With the ever increasing complexity of simulation models, parallel simulation
becomes necessary to perform the simulation within reasonable time bounds.
The built-in parallelism of Parallel DEVS is often insufficient to tackle this problem on its own.
Several synchronization protocols have been proposed, each with their distinct advantages and disadvantages.
Due to the significantly different implementation of both protocols, most Parallel DEVS simulation tools are limited to only one such protocol.
In this paper, we present a Parallel DEVS simulator, grafted on C++11, but based on PythonPDEVS, which supports both conservative and optimistic synchronization.
We evaluate the performance gain obtained by choosing the most appropriate synchronization protocol.
Performance results are compared to adevs, in terms of CPU time and memory usage.
